Verifying Demonstrations

### 2021-06-16 paper/practical-considerations.tex
changes \include to \input in practical-considerations to prevent page breaks

Some of the assumptions that are required for implementing our proposition are 
not yet realized, however, we believe that they soon will be:
ubiquitous usage of smartphones, with an identity credential
signed by some \ac{CA}\footnote{based on \eg governmental ID on a chip as in Estonia, national
  but private as BankID in Sweden, eIDAS in the EU, or self-sovereign
  identities} ,  distance-bounding capabilities\footnote{based on \eg
  3DBS or key-fob technology integration with phones}, and
infrastructure-independent wireless communications\footnote{based on
  \eg NFC (available but inconvenient), bluetooth or WIFI (Briar and
  FireChat have been used in protests), 5G D2D (scalable but needs
  authorization step)}.

@@

\include{performance-subsection}

>>>>

Some of the assumptions that are required for implementing our proposition are 
not yet realized, however, we believe that they soon will be:
ubiquitous usage of smartphones, with an identity credential
signed by some \ac{CA}\footnote{based on \eg governmental ID on a chip as in Estonia, national
  but private as BankID in Sweden, eIDAS in the EU, or self-sovereign
  identities} ,  distance-bounding capabilities\footnote{based on \eg
  3DB-access or key-fob technology integration with phones}, and
infrastructure-independent wireless communications\footnote{based on
  \eg NFC (available but inconvenient), bluetooth or WIFI (Briar and
  FireChat have been used in protests), 5G D2D (scalable but needs
  authorization step)}.

@@

\input{performance-subsection}
